---
title: "Manuscript Analysis"
author: "David John Baker"
date: "30/09/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

This markdown documents the analyses used in the paper "SDRT".

Analyses here reflect comments after presenting this work at SMPC 2019, COGMIR 19, and at Marcus Pearce's Lab Meeting in Fall of 2019.

The text below is used in the Methods, Modeling and Results section of the manuscript.

# Data Import and Cleaning 

```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(viridis)
library(scales)

# Demographic Data
demographic_data <- read_csv("data/aggregate_data/current_demo_table.csv")

# Single Tone Condition
single_tone_condition_table <- read_csv("data/aggregate_data/current_single_table.csv")

# Multi Tone Conditions 
multi_tone_response_table <- read_csv("data/aggregate_data/current_multi_table.csv")
```

# Methods 

```{r}
demographic_data %>%
  mutate(new_age = str_remove_all(string = age, pattern = "\\{\\\\Q0\\\\\\:\\\\")) %>%
  mutate(new_age = str_remove_all(string = new_age, pattern = "\\\\\\}")) %>%
  mutate(age = as.numeric(new_age)) %>%
  mutate(education = str_remove_all(string = education, pattern = "\\{\\\\Q0\\\\\\:\\\\")) %>%
  mutate(education = str_remove_all(string = education, pattern = "\\\\\\}")) %>%
  mutate(gender = str_remove_all(string = gender, pattern = "\\{\\\\Q0\\\\\\:\\\\")) %>%
  mutate(gender = str_remove_all(string = gender, pattern = "\\\\\\}")) %>%
  mutate(AP = str_remove_all(string = AP, pattern = "\\{\\\\Q0\\\\\\:\\\\")) %>%
  mutate(AP = str_remove_all(string = AP, pattern = "\\\\\\}")) %>%
  mutate(weeks_taking = str_remove_all(string = weeks_taking, pattern = "\\{\\\\Q0\\\\\\:\\\\")) %>%
  mutate(weeks_taking = str_remove_all(string = weeks_taking, pattern = "\\\\\\}")) %>%
  mutate(years_teaching = str_remove_all(string = years_teaching, pattern = "\\{\\\\Q0\\\\\\:\\\\")) %>%
  mutate(years_teaching = str_remove_all(string = years_teaching, pattern = "\\\\\\}")) %>%
  mutate(gender = str_to_upper(gender)) %>%
  mutate(gender = str_replace_all(string = gender, pattern = "\\F$", replacement = "FEMALE")) %>%
  select(subject_id,age, education, gender, AP, weeks_taking, years_teaching) -> d_table

d_table %>%
  print(n = nrow(d_table)) 

d_table$age %>% mean()
d_table$age %>% sd()
d_table$age %>% range()

d_table %>%
  group_by(gender) %>%
  tally()

```


# Modeling

Data from this experiment are reported following the three hypotheses listed above.

1. H1: Musical notes that occur more frequently in a musical corpora will be recalled more accurately and quickly than less frequently occurring musical patterns. 
2. H2: Exploratory analysis of computationally derived univariate features. 
3. H3: Mixed effects regression analysis modeling both accuracy and response time using theoretically motivated predictors of information content via computationally derived features. 
Participants were excluded from this study if they performed at chance levels in the single tone condition.
Chance level performance was taken to be indicitive that participants did not have the pre-requisite skills in order to partake in the experiment.
No participants were excluded from the study.

```{r}
single_tone_condition_table %>%
  group_by(subject) %>%
  summarise(mean_score = mean(score)) %>%
  arrange(mean_score)

multi_tone_response_table %>% 
  group_by(subject) %>%
  summarise(mean_score = mean(score)) %>%
  arrange(mean_score)
```

In order to examine the hypothesis that more frequently occurring musical notes will be recalled more accurately and quickly than less frequently occurring notes we adopt the following operationalizations. We define accuracy as the average percent of tones that were correctly identified across a participant’s trial. Response time was measured in milliseconds to respond. Frequency of occurrence is modeled using zeroth order distribution frequency of occurrence in the MeloSol corpus, zeroth order frequency of starting tones in the MeloSol corpus, zeroth order frequency distribution in the Essen Folk Song Collection (Schaffrath 1995). Correlations between reaction time of trials, average accuracy, and the three measures of frequency of occurrence and presented in TABLE 1 with their frequency of distribution displayed in PANEL X. Correlations reported are Spearman rank order. As the experimental paradigm only consisted of a major key prime, scale degrees from minor keys are not included in the frequency count.

* Caclulate average score of each trial across all participants

* Accuracy ~ MeloSol Frequency Count 
* Accuray ~ MeloSol Starting Note Count 
* Accuray ~ Essen Frequnecy Count 

First check for no main effect of key. 

```{r}
#----------------------------------------------------------------------
# Check for No Effect of Key 
single_tone_condition_table %>%
  group_by(stimuli_together) %>%
  summarise(mean_score = mean(score)) %>%
  arrange(desc(mean_score)) %>%
  mutate(key = str_remove_all(stimuli_together, "-.*$")) %>%
  select(mean_score, key) -> effect_of_key

effect_of_key %>%
  ggplot(aes(x = key, y = mean_score)) +
  geom_boxplot()

# No Main Effect of Key 
effect_of_key_model <- aov(mean_score ~ key, data = effect_of_key)
summary(effect_of_key_model)

# Extract mean and sd RT for correct responses 
1066/1482

single_tone_condition_table %>%
  filter(score == 1) %>%
  group_by(scale_degree) %>%
  summarise(mean_rt = mean (rt),
            sd_rt = sd(rt)) %>%
  mutate(z_mean_rt = scale(mean_rt),
         z_mean_sd = scale(sd_rt),
         z_mean_rt_inv = z_mean_rt * -1) -> correct_single_tone_rt
  
```

Import count data for correlation plots

### Hypothesis I 

```{r}
#--------------------------------------------------
# MELOSOL TOTAL FREQUENCY
#--------------------------------------------------
# Total Counts of All Notes 
corpus_counts <- read_csv("data/aggregate_data/for_krum_multi_plot.csv")

# coding error from original 
corpus_counts <- corpus_counts %>%
  select(-scale_degree_f)

# coding error in original 
corpus_counts[corpus_counts$degree == "1-",1] <- "ra"

# 36,000 notes from MeloSol 
sum(corpus_counts$count)

# Set Factor For Graphing 
corpus_counts$scale_degree_f <- factor(corpus_counts$scale_degree, 
                                      levels = c("do","ra", "re", "me", "mi",
                                                 "fa", "fi","sol","le", "la", 
                                                 "te", "ti"))

corpus_counts %>%
  select(scale_degree, scale_degree_f, count, degree) %>%
  rename(melosol_total_count = count) -> melosol_freq_count_table

#--------------------------------------------------
# MELOSOL STARTING PITCH FREQUENCY
#--------------------------------------------------

# First Pitch (Huron, 2006, p. 65, 66) via MeloSol
huron_start_table <- read_csv("data/aggregate_data/huron_start_table.csv")

# 767 Melody Starts 
sum(huron_start_table$counts)

huron_start_table %>%
  rename(scale_degree_pc = scale_degree,
         melody_start_counts = counts) -> huron_start_table

huron_start_table$scale_degree <- c("do","ra", "re", "me", "mi",
                                    "fa", "fi","sol","le", "la", 
                                    "te", "ti")

huron_start_table$scale_degree_f <- factor(huron_start_table$scale_degree, 
                                           levels = c("do","ra", "re", "me", "mi",
                                                      "fa", "fi","sol","le", "la", 
                                                      "te", "ti"))

melosol_freq_count_table %>%
  left_join(huron_start_table) -> melosol_freq_count_table


#-----------------------------------------------------------
# ESSEN TOTAL COUNTS 
# Table of How Many times each SD occurs in Essen 
#------------------------------------------------------------
essen_table <- read_tsv("data/aggregate_data/essen_counts.tsv", col_names = FALSE)
essen_table <- essen_table %>%
  rename(count = X1,
         degree = X2)

melosol_freq_count_table <- melosol_freq_count_table %>%
  left_join(essen_table)

#-------------------------------------------------------------
# Create Correlations Between Avg Correct AND MeloSol (2) and Essen 
# Reaction time included as well ???

# Remove Minor Key Notes due to major prime in Experiment 

melosol_freq_count_table 

single_tone_condition_table %>%
  group_by(scale_degree) %>%
  summarise(mean_score = mean(score),
            sd_score = sd(score)) %>%
  arrange(desc(mean_score)) -> avg_single_tone_score_table

melosol_freq_count_table %>%
  left_join(avg_single_tone_score_table) %>%
  mutate(z_ms_total = scale(melosol_total_count),
         z_ms_start = scale(melody_start_counts),
         z_essen = scale(count),
          z_mean_score = scale(mean_score)) -> h1_table

colnames(h1_table)

h1_table$degree_f <- factor(h1_table$degree, levels = c("1", "1-","2-", "2","3-","3", "3+", "4", "4+", 
                                                    "5-", "5", "6-", "6", "6+", "7-", "7",  "7+"))

h1_table %>%
  left_join(correct_single_tone_rt) -> h1_table

h1_table %>%
  select(starts_with("z"))

#--------------------------------------------
# Calculate Correlations 
h1_table %>%
  # filter(degree != "1-") %>% # Enharmonic
  # filter(degree != "6-") %>% # Remove Minor Notes (Since Major Experiment Prime)
  # filter(degree != "6+") %>% # Remove Minor Notes (Since Major Experiment Prime)
  # filter(degree != "7+") %>%
  # filter(degree != "5-") %>%
  # filter(degree != "3+") %>%
  select(starts_with("z"), mean_score) %>%
  cor(use = "complete.obs", method = "spearman")

# Experimental Correlations 
cor.test(h1_table$z_mean_score, h1_table$z_ms_total, method = "spearman", alternative = "greater")
cor.test(h1_table$z_mean_score, h1_table$z_ms_start, method = "spearman", alternative = "greater")
cor.test(h1_table$z_mean_score, h1_table$z_essen, method = "spearman", alternative = "greater")

# Corpus Correlations (Check MANUSCRIPT)
cor.test(h1_table$z_ms_total, h1_table$z_essen, method = "spearman", alternative = "greater")
cor.test(h1_table$z_ms_start, h1_table$z_essen, method = "spearman", alternative = "greater")
cor.test(h1_table$z_ms_start, h1_table$z_ms_total, method = "spearman", alternative = "greater")

colors_h1 <- c("z_ms_total" = "green", 
            "z_ms_start" = "blue", 
            "z_essen" = "red",
            "z_mean_score" = "black")

h1_table %>%
  filter(!is.na(degree_f)) %>%
  ggplot(aes(x = degree_f)) +
  geom_point(aes(y = z_ms_total, color = "z_ms_total"),   group  = 1) +
  geom_line(aes(y = z_ms_total,  color = "z_ms_total"),  group = 1) +
  geom_point(aes(y = z_ms_start, color = "z_ms_start"),  group = 2) +
  geom_line(aes(y = z_ms_start,  color = "z_ms_start"),  group = 2) +
  geom_point(aes(y = z_essen,  color = "z_essen"),    group = 3) + 
  geom_line(aes(y = z_essen,  color = "z_essen"),     group = 3) +
  geom_point(aes(y = z_mean_score, color = "z_mean_score"),group = 4) + 
  geom_line(aes(y = z_mean_score, color = "z_mean_score"), group = 4) +
  theme_minimal() +
  labs(title = "Normalized Scale Degree Frequency and Mean Accuracy",
       subtitle = "CHECK LABELS",
       x = "Scale Degree",
       y = "z score",
       color = "Legend") +
      scale_color_manual(values = colors_h1,
                         labels = c("All Notes in MeloSol",
                                    "Starting Notes in MeloSol",
                                    "All Notes in Essen",
                                    "Mean Accuracy of Experiment")) -> mean_rt_corpus_figure

mean_rt_corpus_figure

ggsave(filename = "figures/mean_rt_corpus.png", 
       mean_rt_corpus_figure, 
       width = 9, height = 4, units = "in")

#--------------------------------
# Reaction Time and Accuracy 
colors_h1_behavioral <- c("z_mean_score" = "black",
            "z_mean_rt_inv" = "blue")

# RT Correlations 
cor.test(h1_table$z_mean_rt_inv, h1_table$z_mean_score, method = "spearman", alternative = "greater")

h1_table %>%
  filter(!is.na(degree_f)) %>%
  ggplot(aes(x = degree_f)) +
  geom_point(aes(y = z_mean_score, color = "z_mean_score"),group = 1) + 
  geom_line(aes(y = z_mean_score, color = "z_mean_score"), group = 1) +
  geom_line(aes(y = z_mean_rt_inv, color = "z_mean_rt_inv"), group = 2) +
  geom_line(aes(y = z_mean_rt_inv, color = "z_mean_rt_inv"), group = 2) +
  theme_minimal() +
  labs(title = "Normalized Mean Accuracy and Inverted Reaction Time",
       subtitle = "Spearman's RHO (XX) = .861",
       x = "Scale Degree",
       y = "z score",
       color = "Legend") +
      scale_color_manual(values = colors_h1_behavioral,
                         labels = c("Mean Accuracy All Trials",
                                    "Inverted RT of Correct Trials")) -> mean_rt_corpus_figure_behavioral

mean_rt_corpus_figure_behavioral

ggsave(filename = "figures/mean_rt_corpus_behavioral.png", 
       mean_rt_corpus_figure_behavioral, 
       width = 9, height = 4, units = "in")
```

### Hypothesis II 

* Import in all theoretical variables of interest
* Plot each feature against mean performance of variable 


* IDYOM - Mean IC 
* IDYOM - Cumulitive IC 
* IDYOM -- Three Viewpoints

* FANTASTIC 

Three separate IDyOM models were run, the first using CPINT, the second CPINTREF, and the third using a combination of the CPINT and CPINTREF viewpoints. The information content as determined for each n-gram within each model was averaged.


```{r}
#======================================================================================================
# FANTASTIC DATA
fantastic_features <- read_csv("experiment_materials/new_stimuli/MelodyFeatures.csv")
#------------------------------------------------------------------------------------
# Clean FANTASTIC 
#--------------------------------------------------
fantastic_features %>%
  rename(stimulus = file.id) -> fantastic_features


fantastic_features$stimulus <- gsub(pattern = "m",replacement = "", fantastic_features$stimulus)
fantastic_features$stimulus <- gsub(pattern = "ono",replacement = "", fantastic_features$stimulus)
fantastic_features$stimulus <- gsub(pattern = "_",replacement = " ", fantastic_features$stimulus)
fantastic_features$stimulus <- str_trim(fantastic_features$stimulus, side = "right")

fantastic_features$stimulus

View(fantastic_features)
#------------------------------------------------------------------------------------
# IDYOM Data 

# Model 1

# Model 2

# Model 3





#--------------------------------------------
# OLD DATA
# Import Data ####
idyom_computations <- read_csv("data/aggregate_data/idyom_computation.csv")

View(idyom_computations)

#--------------------------------------------------
# Krumhansl 1982 ratings
krumhansl <- c(6.35,2.23,3.48,2.33,4.38,4.09,2.52,5.19,2.39,3.66,2.29,2.88)
scale_degree <- c("do","ra","re","me","mi","fa","fi","sol","le","la","te","ti")
krummy <- data.frame(krumhansl,scale_degree)

cogmir_counts <- read_csv("experiment_materials/stimuli_lists/cogmir_stimuli.csv")
#--------------------------------------------------
# Join Perceptal Data to CogMIR counts

# Drop X1
multi_table %>%
  select(-X1) -> multi_table

# Clean Up Stimulus Variable For Merge
multi_table$stimulus <- gsub(pattern = "_",replacement = " ", x = multi_table$stimulus)

cogmir_counts %>%
  rename(stimulus = Pattern) -> cogmir_counts

multi_table %>%
  left_join(cogmir_counts) -> SLH_table

idyom_computations$stimulus <- gsub(pattern = "_", replacement = " ",x = idyom_computations$stimulus)

SLH_table %>%
  left_join(idyom_computations) -> idyom_analysis_table 

idyom_analysis_table

#======================================================================================================
idyom_analysis_table %>%
  left_join(fantastic_features) -> modeling_table

for_groups <- as.data.frame(names(modeling_table))

for_groups

#write_csv(x = for_groups, path = "imgs/group_plots_output.csv")

#--------------------------------------------------
# Names for Table

for_graph_lables <- read_csv("pilot_imgs/group_plots_input.csv",
                             col_names = c("names","theory"))
for_graph_lables





```



```{r}
# Scratch 
# Only Complete Trials 
multi_tone_response_table %>%
  group_by(subject, stimulus) %>%
  mutate(trial_score = mean(score)) %>%
  filter(trial_score == 1) %>%
  ungroup(subject, stimulus) %>%
  group_by(serial_order, stimulus) %>%
  mutate(mean_rt = mean(rt)) %>%
  ggplot(aes(x = serial_order, y = mean_rt, color = stimulus)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~trial_length)

  



# how many complete trials do i have
# Does that change over n increase 

multi_tone_response_table %>%
  mutate(unique_trial = paste(subject, stimulus)) %>%
  left_join(trial_totaller) %>%
  group_by(unique_trial) 



multi_tone_response_table %>%
  filter(trial_length == 3) %>%
  group_by(serial_order, stimulus) %>%
  mutate(mean_score = mean(score),
         mean_rt = mean(rt)) %>%
  ggplot(aes(x = serial_order, y = mean_score, color = stimulus)) +
  geom_point() +
  geom_smooth()


multi_tone_response_table %>%
  filter(trial_length == 3) %>%
  group_by(serial_order, stimulus) %>%
  mutate(mean_score = mean(score),
         mean_rt = mean(rt)) %>%
  ggplot(aes(x = serial_order, y = mean_rt, color = stimulus)) +
  geom_point() +
  geom_smooth()

```





